PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed the comment about anxiety and depression from Katie

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

>>>>

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 0 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )
